---
title: 'SSBU: Data Science Tierlist'
author: "Clurkastas"
date: "6 10 2019"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls()) #delete workspace
knitr::opts_chunk$set(echo = F, include = F)

# Packages
library(tidyverse)
library(rvest) #harvesting unstructured data
library(httr) #benötigt für RSelenium?
library(RSelenium) #load more of website (Scroll down)
library(roperators) #counting words
library(xml2)
library(stringr) #searching for figthers names
```

## Data Gathering
```{r data}

# Navigate to page with RSelenium
url <- "https://www.youtube.com/results?search_query=ssbu+grand+finals&sp=CAI%253D"
driver <- rsDriver(browser=c("firefox"))
remote_driver <- driver[["client"]]
#remote_driver$open() #öffnet nur leeres fenster
remote_driver$navigate(url)

#Runterscrollen um mehr Daten zu bekommen
webElem <- remote_driver$findElement("css", "body") #body auswhählen
for (i in 1:30){
  webElem$sendKeysToElement(list(key = "end")) #scrollen
  Sys.sleep(3) #laden lassen damit erneut heruntergescrollt werden kann
}

# Relevante Daten (Überschriften) aus der Seite ziehen
alldata <- xml2::read_html(remote_driver$getPageSource()[[1]])%>% #transform to html
  rvest::html_nodes("#video-title") #extract title nodes
links <- alldata %>%
  html_attr("href") #extract link
names <- alldata %>%
  html_attr("title") #extract title

#Close connection
remote_driver$close() #bzw window
rm(remote_driver)
rm(webElem)
rm(driver)

#Jetzt hab ich Daten!
dat1 <- as.data.frame(cbind(links,names))
str(dat1)

#zuerst: Daten cleanen
dat1 <- dat1[dat1$names!="",] #ohne Titel ("") raus
dat1 <- dat1[is.na(dat1$names)==F,] # ohne Titel (NA) raus
dat1$names <- as.character(dat1$names)
datalength <- length(dat1$names) 

```

To gather information for my tier list, I used the RPackage "RSelenium". It gathered `r datalength` video titles from [this Youtube link](`r url`). The link was created by searching for "SSBU grand finals" ordered by date. 

```{r cleaning}
#als nächstes: Charakternamen rausziehen
library(stringr)

#namen von: https://www.ssbwiki.com/Super_Smash_Bros._Ultimate
namechecklist <- list("Dr. Mario","Mario","Luigi","Peach",
     "Rosalina", "Bowser Jr.", "Bowser", "Yoshi",
     "Donkey Kong","Diddy Kong","Zelda", "Ganondorf",
     "Sheik","Young Link", "Toon Link", "Link",
     "Dark Samus",c("ZSS","Zero Suit Samus"), "Samus", "Kirby","Meta Knight",
     "King Dedede", "Fox", "Captain Falcon", "Falco", "Wolf", 
     "Pikachu", "Jigglypuff","Pichu","Mewtwo",
     c("Pokemon Trainer","Squirtle","Ivysaur","Charizard"),
     "Lucario","Greninja","Ness",
     "Lucas","Ice Climbers","Marth","Roy",
     "Ike","Lucina","Robin","Corrin",
     c("Game and Watch","Game & Watch","G&W","G and W"),
      "Palutena","Dark Pit", "Pit",
     "Wario",c("Olimar","Alph"),c("ROB","R.O.B"),"Villager",
     c("Wii Fit","WFT"), "Little Mac",
     "Shulk", "Duck Hunt",
     "Snake","Sonic","Mega Man","Pac-Man",
     "Ryu", "Cloud", "Bayonetta",
     "Mii Brawler", "Mii Swordfighter", "Mii Gunner",
     "Daisy", "Piranha Plant", 
     c("King K. Rool","King K Rool"), "Ridley",
     "Incineroar", "Chrom", "Isabelle",
     "Inkling", "Ken", "Simon", "Richter",
     "Joker", "Hero", c("Banjo","Kazooie"), "Terry")
str(namechecklist)

# für jeden Listeneintrag schauen, ob das Muster erkennbar ist :)
y <- list(NA,NA)
colnames <- c(NA,NA)
for (i in 1:length(namechecklist)){
  y[[i]] <- str_detect(dat1$names, regex(paste(namechecklist[[i]], collapse = '|'), ignore_case = TRUE))
  num = 0
  for (j in 1:length(y[[i]])){
    if(y[[i]][j]==TRUE){
      print(paste0("wird ersetzt",num))
      num <- num+1
      dat1$names[j] <- str_replace_all(string = dat1$names[j], 
                                       pattern = namechecklist[[i]], 
                                       replacement = " ")[1] #replace patterns so that "mario" and "dr. mario" (etc) don't interfere
                }
      }
  dat1[,i+2] <- y[[i]]
  colnames[i] <- as.character(namechecklist[[i]][1])
}
names(dat1) <- c("link","title",colnames)

summary(dat1)
```

After that I had to clean out the data. For this I searched for all fighter names inside the video titles. It was important to e.g. first search for "Dr. Mario", deleting this part of the string, and then search for "Mario", because otherwise the data would not have been correct. Additionally, I needed to search for multiple variants of a name, e.g. "ZSS" and "Zero Suit Samus" or "Olimar" and "Alph". 

```{r more cleaning}

dat1 <- dat1[,-c(1,2)]
for (i in 1:length(dat1[1,])){
  dat1[,i] <- as.numeric(dat1[,i])
}
wtf <- t(dat1) #transponieren

summary(wtf)
sapply(wtf, class) 

rowSums <- as.integer(rowSums(wtf))
summary(rowSums)
dat2 <- data.frame(cbind(colnames,rowSums))
dat2$rowSums <- as.character(dat2$rowSums)
dat2$rowSums <- as.numeric(dat2$rowSums)


dat3 <- dat2 %>% 
  arrange(-rowSums)
dat3$tier<-NA
dat3$tier[dat3$rowSums>24] <- "S"
dat3$tier[dat3$rowSums<=24 & dat3$rowSums>16] <- "A"
dat3$tier[dat3$rowSums<=16 & dat3$rowSums>8] <- "B"
dat3$tier[dat3$rowSums<=8 & dat3$rowSums>4] <- "C"
dat3$tier[dat3$rowSums<=4 & dat3$rowSums>2] <- "D"
dat3$tier[dat3$rowSums<=2 & dat3$rowSums>-1] <- "E"
dat3$tier <- as.factor(dat3$tier)
dat3$tier = factor(dat3$tier,levels(dat3$tier)[c(5,4,3,2,1,6)])
summary(dat3)
dat3$rowSums

dat3 %>% 
  ggplot(aes(y=colnames, x=rowSums, col=tier)) +
  #facet_wrap(~tier, scales = "free_y") +
  geom_point() +
  geom_text(aes(label=colnames),hjust=-0.1, vjust=0)+
  labs(x=NULL,y=NULL) +
  theme(axis.text.y = element_blank(), legend.position = "none")


#Compare tier list to ZeRo's tier list (https://smash-tier-list.com/ultimate)

dat3$colnames <- as.character(dat3$colnames)
dat3$tierZeRo <- NA
dat3$tierZeRo[dat3$colnames=="Little Mac"] <- 1
C_tier <- c("Ridley","Bowser Jr.","Piranha Plant","Game and Watch")
dat3$tierZeRo[grep(x=dat3$colnames,pattern = paste(C_tier, collapse = '|'))] <- 2
A_tier <- c("Ike","Palutena","Young Link", "Snake", "Roy",
            "Chrom", "ROB", "Shulk", "Pokemon Trainer",
            "Marth", "Link", "Mega Man", "Yoshi", "Lucario",
            "Ness", "Cloud", "ZSS", "Sonic", "Pac-Man",
            "Lucas", "Mii Swordfighter")
dat3$tierZeRo[grep(x=dat3$colnames,pattern = paste(A_tier, collapse = '|'))] <- 4
#B-tier after A because of "Link"
B_tier <- c("Ganondorf","Corrin","Falco","Mario","Dr. Mario",
            "Bayonetta","Captain Falco","Meta Knight","Richter","Simon",
            "Toon Link","Samus","Dark Samus","Wii Fit","Mii Gunner",
            "Luigi", "Donkey Kong", "Bowser", "Villager",
            "Isabelle", "Ryu", "Ken", "Ice Climbers", "Mewtwo",
            "Diddy Kong", "Kirby", "Incineroar", "Robin", "Duck Hunt",
            "Rosalina", "Sheik", "Zelda", "Jigglypuff",
            "King Dedede", "King K. Rool",
            "Pit", "Dark Pit", "Mii Brawler")
dat3$tierZeRo[grep(x=dat3$colnames,pattern = paste(B_tier, collapse = '|'))] <- 3
S_tier <- c("Pichu", "Peach", "Daisy", "Olimar", "Lucina",
            "Pikachu", "Wolf", "Fox", "Wario", "Inkling", "Greninja")
dat3$tierZeRo[grep(x=dat3$colnames,pattern = paste(S_tier, collapse = '|'))] <- 5
dat3$tierZeRo <- as.factor(dat3$tierZeRo)
levels(dat3$tierZeRo) <- c("D","C","B","A","S")

dat3$tierZeRo <- as.numeric(dat3$tierZeRo)
dat3$tier <- as.numeric(dat3$tier)
cor(dat3$tierZeRo, dat3$rowSums, use="pairwise.complete.obs")
cor(dat3$tierZeRo, dat3$tier, use="pairwise.complete.obs")
cor(dat3$tier, dat3$rowSums, use="pairwise.complete.obs")
table(dat3$tierZeRo, dat3$tier)

#log10 rowSums (Ausreißer Ness)
dat3$log10rowSums <- log10(dat3$rowSums)
dat3$log10rowSums[dat3$rowSums==0] <- NA
cor(dat3$tierZeRo, dat3$log10rowSums, use="pairwise.complete.obs")

names(dat3) <- c("fighter","amount","tier_data","tier_ZeRo","amount_log10")

```

# Analysis

Eventually, I got a sum of observations for each character in SSBU. I added the tier list information from [ZeRo's tier list](https://smash-tier-list.com/ultimate) to compare my results to external information. From all the information gathered I created some interesting charts:

```{r analysis, echo=T}
dat3 %>%
  ggplot(aes(y=tier_ZeRo, x=amount)) +
  geom_jitter() +
  geom_smooth(method = "lm") 


```

