---
title: 'SSBU: Data Science Tier List'
author: "Clurkastas"
date: "6 10 2019"
output: 
  html_document:
    number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list=ls()) #delete workspace
knitr::opts_chunk$set(echo = F, include = F, warning=F)

# Packages
library(tidyverse)
library(rvest) #harvesting unstructured data
library(httr) #benötigt für RSelenium?
library(RSelenium) #load more of website (Scroll down)
library(roperators) #counting words
library(xml2)
library(stringr) #searching for figthers names
library(kableExtra)

datalength <- read.csv("datalength.csv")[2]
```

# Data Gathering

To gather information for my tier list, I used the RPackage "RSelenium". It gathered `r datalength` video titles from [this Youtube link](https://www.youtube.com/results?search_query=ssbu+grand+finals&sp=CAI%253D). The link was created by searching for "SSBU grand finals" ordered by date. 

After that I had to clean out the data. For this I searched for all fighter names inside the video titles. It was important to e.g. first search for "Dr. Mario", deleting this part of the string, and then search for "Mario", because otherwise the data would not have been correct. Additionally, I needed to search for multiple variants of a name, e.g. "ZSS" and "Zero Suit Samus" or "Olimar" and "Alph". 

```{r load data}
#außerhalb dieses Dokuments wurde alles heruntergeladen und gecleant, damit das dokument hier öfter geknitten werden kann
dat4 <- read.csv(file="SSBU_youtube_tierlist.csv")

overlap <- dat4$fighter[abs(dat4$tier_data-dat4$tier_ZeRo)==0 & is.na(abs(dat4$tier_data-dat4$tier_ZeRo))==F]
dat4$overlap_dich <- (abs(dat4$tier_data-dat4$tier_ZeRo)==0 & is.na(abs(dat4$tier_data-dat4$tier_ZeRo))==F)
dat4$difference_tlists <- abs(dat4$tier_data-dat4$tier_ZeRo)
```

# Analysis

Eventually, I got a sum of observations for each character in SSBU. I added the tier list information from [ZeRo's tier list](https://smash-tier-list.com/ultimate) to compare my results to external information. From all the information gathered I created some interesting charts:

## Chart with ZeRo's Tier list and amount of mentioning in grand final videos

```{r analysis 01, include=T}
dat4 %>% 
  ggplot(aes(x=tier_ZeRo, y=amount, 
             col=as.factor(tier_ZeRo))) +
  geom_text(aes(label=fighter),
            position = position_jitter(w = 0.4, h=0.1),
            size=3)+
  labs(y="Amount of Mentioning in Grand Finals Videos",x="ZeRo's Tier List") +
  theme(legend.position = "none")+
  geom_smooth(method = "lm") 
cor_amountZeRo <- cor(dat4$tier_ZeRo, 
                     dat4$amount, 
                     use="pairwise.complete.obs")
```

The correlation here is `r round(cor_amountZeRo, 2)`

## Same chart but log10(amount)

```{r analysis 02, include=T}
dat4 %>% 
  ggplot(aes(x=tier_ZeRo, y=amount_log10, 
             col=as.factor(tier_ZeRo))) +
  geom_text(aes(label=fighter),
            position = position_jitter(w = 0.4, h=0.1),
            size=3)+
  labs(y="log10(Amount of Mentioning in Grand Finals Videos)",x="ZeRo's Tier List") +
  theme(legend.position = "none")+
  geom_smooth(method = "lm") 
cor_log10ZeRo <- cor(dat4$tier_ZeRo, 
                     dat4$amount_log10, 
                     use="pairwise.complete.obs")
```

The correlation here is `r round(cor_log10ZeRo, 2)`

## Data Science Tier List (compared with ZeRo's) graphics

Bases on the amounts of mentioning I made some tier groups myself. For this I just had to decide on the cut-off values between the tier list levels.

```{r analysis 03, include=T}

dat4 %>% 
  ggplot(aes(x=tier_data, y=amount, 
             col=as.factor(tier_data))) +
  geom_text(aes(label=fighter),
            position = position_jitter(w = 0.4, h=0.1),
            size=3)+
  labs(y="Amount of Mentioning in Grand Finals Videos",x="Data Science Tier List") +
  theme(legend.position = "none")
cor_amountZeRo <- cor(dat4$tier_ZeRo, 
                     dat4$amount, 
                     use="pairwise.complete.obs")

dat4 %>% 
  ggplot(aes(x=tier_data, y=amount_log10, 
             col=as.factor(tier_data))) +
  geom_text(aes(label=fighter),
            position = position_jitter(w = 0.4, h=0),
            size=3)+
  labs(y="log10(Amount of Mentioning in Grand Finals Videos)",x="Data Science Tier List") +
  theme(legend.position = "none")
cor_amountZeRo <- cor(dat4$tier_ZeRo, 
                     dat4$amount, 
                     use="pairwise.complete.obs")

dat4 %>% 
  ggplot(aes(x=tier_ZeRo, y=tier_data
             )) +
  #facet_wrap(~tier, scales = "free_y") +
  geom_text(aes(label=fighter, col=overlap_dich),
            position = position_jitter(w = 0.5, h=0.5),
            size=3)+
  labs(y="Data Science Tier List",x="ZeRo's Tier List") +
  theme(axis.text.y = element_blank(), legend.position = "none") +
  geom_smooth(method = "lm") 
cor_ZeRodata <- cor(dat4$tier_data, 
                     dat4$tier_ZeRo, 
                     use="pairwise.complete.obs")



```

In the chart you can see ZeRo's tier list on the x-axis and my tier list on the y-axis. Red dots are values of total overlap. Both tier lists agree totally on the following fighters: `r paste(overlap, collapse = ', ')`. The correlation is `r round(cor_ZeRodata,2)`

```{r analysis 04, include=T}

dat4 %>% 
  ggplot(aes(x=tier_ZeRo, y=tier_data)) +
  geom_text(aes(label=fighter, col=as.factor(difference_tlists)),
            position = position_jitter(w = 0.5, h=0.5),
            size=3)+
  labs(y="Data Science Tier List",x="ZeRo's Tier List") +
  theme(legend.position = "none") +
  geom_smooth(method = "lm") 


dat5 <- dat4[is.na(dat4$tier_ZeRo)==F,]
table_dat_list <- cbind(c("S","A","B","C","D"),
                        c(paste(dat5$fighter[dat5$tier_data==5], collapse = ', '),
                          paste(dat5$fighter[dat5$tier_data==4], collapse = ', '),
                          paste(dat5$fighter[dat5$tier_data==3], collapse = ', '),
                          paste(dat5$fighter[dat5$tier_data==2], collapse = ', '),
                          paste(dat5$fighter[dat5$tier_data==1], collapse = ', ')))



```

# The Data Science Tier List

`r kable_styling(knitr::kable(table_dat_list), "striped", position = "left")`



